---
title: "Hello World!"
description: |
  New blog using Distill!
author:
  - name: Jay Lee
date: 2021-11-07
date_prefix: TRUE # adds date for sorting
draft: FALSE
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

Trying [Distill](https://rstudio.github.io/distill) as a new blogging backend, replacing blogdown/hugo. I don't really need all the customization from blogdown/theme, and don't really want to deal w/ dependencies. From RStudio [post](https://www.rstudio.com/blog/distill/):

>> Importantly, Distill websites are built without any kind of static site generator (like Jekyll or Hugo), which means that Distill websites offer users the bliss of building a website without any additional software dependencies (this means, all you need is R and the distill package to make it work).


```{r, plot-test}
head(mtcars)
plot(mtcars)

```

Notables so far ([reference](https://themockup.blog/posts/2020-08-01-building-a-blog-with-distill/).
):

- really like the simplicity...can truly focus on creating posts
- no addin for new post, but I'm guessing there will be one if I look harder
  - new post by create_post()
- seems to need to knit each post before it showing as a post
- had to re-create github PAT
- had to update gh package (kept getting complaint about newly created PAT)